\chapter*{ONE}

Earlier this year I woke up to find myself in a hospital in San Francisco. City by the Bay. City of Dreams. I had been dreaming for a very long time.

The calendar hung on the wall was the first thing I saw, but it was too far away to see what day it was, even with the ambient lights outlining the ceiling. Pretty fancy lights, I hadn't seen anything like that in a hospital before. I had woken up in the middle of the night. I got up, and after a certain amount of convincing was done, to get my limbs amicable to movement, I managed to get myself near the calendar on the wall. I was still too far away to see the day, but at the top of the page, in larger bold font, I could read\\


2027 --- YOUR LUCKY YEAR!
\\

\noindent
I remember the moment very well. I moved closer to the wall and stood still for several seconds before starting to rip through the calendar. It was no joke! The date hadn't been set to April 1st or anything like that, and what's more, the entire calendar was for the year 2025, indeed. Someone had played a very elaborate practical joke on a fallen man. How terrible of them. I couldn't think of any member of my family who had the malicious ingenuity necessary for this sort of thing, but some of my friends certainly possesed extravagant quantities of both malice and genius. Everything was alright. I had recovered from my fall and people were playing jokes on me. Life was going to be as chill as a man could hope.

I sat on the bed and recalled falling from our front porch steps on 37th Street in Georgetown: the slip, the fright, everything. I remember being worried briefly about how violent I was moving towards the ground, before I passed out. I remember the scene of the rain hitting the old-world paving in the street and the cobbled paths in the garden, drenching the leaves that had fallen on the sidewalk that season, grinding them slowly into the stone, and falling on the trees that stood in noble abundance everywhere in Georgetown.

That was the last sight I remember before I went to sleep in October 2012. I would not find out about my 15 year coma until later in the night. For now I set about exploring the fascinating hospital environment: I was very thirsty, there had to be a cute nurse somewhere to help fix this.

I walked down the hallway from my room. The corridor leading from a set of rooms down to a bigger lobby. The lighting was sparse, the walls were white, covered in paintings and moving pictures. LCD photo albums lined the wall on both sides. The technology had become accessible to the point of obscurity.
In my stupor I made note to check the prices on these things on ebay, last I remembered they weren't exactly cheap enough to cover hospital corridors with. I didn't know at the time that liquid crystal was now cheaper than paper. The imports from China and Taiwan had become cheaper than American paper. But I am getting ahead of myself, I didn't know any of this as I walked between the walls and emtpy, glowing cubicle stations.

I dragged myself further down the hallway and noticed the patient rooms, which were part see-through, and the patients lying on the beds in the middle, each bed with a set of devices neatly laid on a rack beside it, and a large number of displays on the wall. All that equipment! Where was I? I am a Computer Science major and I had never seen such a sight. Everything had this clean Apple Inc feeling to it that was starting to become acutely unnerving, and I moved faster to the doors up ahead, taking a few agonized steps, when someone screamed from behind a cubicle to the right:

``OH MY GOODNESS -- Mr.~Fontaine -- what are you doing -- you're \textit{awaiike}! Securitay! SECURITAY!!''.

I'd had little time to compose a response or ask the nurse where the heck she got her accent when I was attacked by several heavy people, and suddenly found myself on the floor. The men who assaulted me were no joke. They were not nurses, or ordinary ``securitay''. They carried submachine guns fitted in holsters on their backs, and looked like a modern video game version of an elite strike team, kneepads ands masks and everything.

With no little irreverence they carried me back to my cell (and it was a cell, you better believe), put me in bed again, then tied my ankles with plastic cuffs to the bed. It was like I had tried to assasinate the President. We use to have Presidents, you must have heard. Back in the good old US of A, we had primaries and general elections, and presidents. But we'll come to all that. I've promised myself to not throw everything at you all at once, God knows, you will have trouble enough swallowing any of it either way. Back to the hospital. The men surrounded my bed, waiting for the doctors to arrive.

``Sir, you are not to move at all. You have just violated rules of the ward. Please remain calm or we will be forced to respond with force''. The guard who was speaking was extremely courteous. Very funny man apparently. I wanted to point out that they had already used a fair amount of physical force, then I realized these people had appeared out of nowhere. Later I would find out that the nurses and guards had to be kept out of sight, their stations were literally hidden in the walls. The psychological aspect of mainting control in certain places, without the appearance of intrusion, is a very important principle of the current system. If you've been in the city, you would know. You must know. 

``I just walked down to-- ''

``Sir you will remain quiet please, you are disturbing the patients.'' the same guard hissed back. Then I saw the patients. The ones nearby, they had been awoken by the little ruckus we caused.

The nurses were now flooding their rooms, administering some sort of calming drug to put them back to sleep. They smiled at the nurses and extended their arms for the shots, weak, grateful smiles that were as ghastly as they were genuine. I shut up immediately. I could see through the plastic walls of the cells they kept us in and I did not know what was going on, but I did feel very good about it. They looked at me. The patients. They had the biggest eyes, staring at me through the walls as they passed out. They were falling asleep thinking about me. I couldn't sleep at all.

No--one had ever been disciplined like that before them. My unknowing act of heresy had elevated me to cult status among the drug--controlled population in the ward. I was a character to be wondered at. The sort of person you discuss the next day, trying to figure out what was went wrong in his head. 

The doctors finally stormed in, their faces ready to witness a miracle.

``Tyler! Tyler -- Mr.~Fontaine\ldots welcome back! We can't \textit{believe} this, you did it! I knew you would. Please forgive our\ldots excitement, something like this doesn't happen here every day\ldots''.

The man speaking identified himself as Dr.~Shields, insisted that I call him Mike instead, and broke the news to me that I was in fact, in California, aroused from a long-term coma. I had opened my eyes a week before, after fifteen years of deep sleep, of which I spent ten in Marin County, in the City of San Francisco. The hospital was specialized in my condition, and had an endowment made specially for my case by an anonymous professor back in Georgetown. The doctors  had come  in one morning to find me staring at the ceiling, but still asleep. Tonight I had decided to rise out of that sleep for no apparent reason than to get a drink of water. This fact would remain an hefty source of amusement for the doctors, who were looking in my direction as you would look at a man walking on thin air. The news vans were on their way. I was a continuation of the unassailable reportoire of medical miracles reported by the National Health Service, I would soon come to know. I was evidence the government was not only supreme but unquestionable in its administration of its healthcare program, as in all other areas of Federal Responsibility. I was a miracle of good government, that needed to be given all the publicity and attention it deserved. Right then I knew nothing at all. There was too much to know all at once. I just wanted to fall asleep again.

\chapter*{TWO}

I am not hoping you will believe all of this, what I've written, what I'm going to write. 

I don't even know if anyone will ever get this, but I know it must be written. At times I will sound insane, but I'm not crazy. You haven't seen crazy. Crazy never sat with you at a dinner table and handed you the ketchup bottle and asked you about your customer support experience with the dream-sex machines. I believe in fate -- you are meant to believe or not to believe. But it is your decision, you know what you know, and you will be responsible for it, and everything that comes of it. If you read through this and start thinking that I'm getting a wee bit over the top, you must understand that you are reading the work of a human being on the brink of collapse.

To give you an idea, dear reader, there is a dead man being eaten by two K-9 police dogs outside the diner I'm in right now, and the officers are sitting in their cruiser writing up the case, the dogs are tearing out chunks of cheek and bones, ripping at his limp shoulders, and people are walking by with Hershey's ice cream cones and paper coffee cups. They're hurrying their children along like it's nothing serious but it's time to go home. They steal quick glances and move on, because we are in the City.

I've decided to write as I go. There may not be time enough to write everything down. I've learnt to follow the signs, and write them down too, so I don't forget. Scribbled memos written everywhere in my notes. Just bear with me. I'll try to explain everything as I write.


